Msc Thesis Figures

### 2020-08-21 docs/msc_thesis_figures.Rmd
updates fig

trans_biplot <- ggbiplot(Trans_Pca, scale = 1,
                         obs.scale = 1, var.scale = 1,
                         groups =  as.factor(trans_memberships),
                         ellipse = T, circle = TRUE) +
  scale_color_manual(name = "Profiles",
                     values = c('#1f78b4','#33a02c','#b2df8a','#a6cee3'), 
                     labels = c("Urbain Spread/Deforestation",
                                "Agricultural Expansion/Deforestation",
                                "Agricultural Expansion/Fragmentation", 
                                "Urban Spread/Agricultural Loss")) +
  theme(panel.background = element_rect(fill = "white", colour = "grey50"),
        legend.direction = 'horizontal', legend.position = 'top') +
  ggtitle("PCA of Municipality profiles")

@@

vals_biplot <- ggbiplot(Values_Pca, scale = 1,
                        obs.scale = 1, var.scale = 1,
                        groups = as.factor(values_memberships),
                        ellipse = T, circle = TRUE) +
  scale_color_manual(name = "Profiles",
                     values = c("#33A02C", "#B2DF8A", "#FF7F00", "#CAB2D6", "#6A3D9A"), 
                     labels = c("Forest - Agriculture",
                                "Forest - Dominant",
                                "Agriculture - Dominant",
                                "Urban - Medium Density", 
                                "Urban - High Density"))+
  theme(panel.background = element_rect(fill = "white", colour = "grey50"),
        legend.direction = 'horizontal', legend.position = 'top') +
  ggtitle("PCA of Municipality profiles")

>>>>

trans_biplot <- ggbiplot(Trans_Pca, scale = 1,
                         obs.scale = 1, var.scale = 1,
                         groups =  as.factor(trans_memberships),
                         ellipse = T, circle = TRUE) +
  scale_color_manual(name = "Profiles",
                     values = c('#1f78b4','#33a02c','#b2df8a','#a6cee3'), 
                     labels = c("Urbain Spread/Deforestation",
                                "Agricultural Expansion/Deforestation",
                                "Agricultural Expansion/Fragmentation", 
                                "Urban Spread/Agricultural Loss")) +
  theme(panel.background = element_rect(fill = "white", colour = "grey50"),
        legend.direction = 'horizontal', legend.position = 'top') +
  ggtitle("PCA of Municipality profiles") +
  theme(legend.box.background = element_blank(),
        panel.border = element_rect(fill = NA),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 8))
#trans_biplot

@@

vals_biplot <- ggbiplot(Values_Pca, scale = 1,
                        obs.scale = 1, var.scale = 1,
                        groups = as.factor(values_memberships),
                        ellipse = T, circle = TRUE) +
  scale_color_manual(name = "Profiles",
                     values = c("#33A02C", "#B2DF8A", "#FF7F00", "#CAB2D6", "#6A3D9A"), 
                     labels = c("Forest - Agriculture",
                                "Forest - Dominant",
                                "Agriculture - Dominant",
                                "Urban - Medium Density", 
                                "Urban - High Density"))+
  theme(panel.background = element_rect(fill = "white", colour = "grey50"),
        legend.direction = 'horizontal', legend.position = 'top') +
  ggtitle("PCA of Municipality profiles")  +
  theme(legend.box.background = element_blank(),
        panel.border = element_rect(fill = NA),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))
